---
title: "Final Assesment R4DS Waikato"
author: "Your Name (Original by Greg Wilson, adopted for teaching by Thomas Koentges)"
date: '2022-06-08'
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(lubridate)
```

Use your database containing the data of the file `toronto-covid-2021-01-04.csv` (which contains reports of COVID-19 cases in Toronto) to load a presentation called `covid`. Alternatively, load the this file directly and create a tibble called `covid`.

```{r read_data}
covid <- read_csv("data/toronto-covid-2021-01-04.csv")
```

Convert the values in the `gender` column to lower case; replace all "unknown" gender entries with `NA`; and then convert the entire column to a factor.
Do not overwrite `covid`, but instead display the result inline.

```{r unknown_as_na}
covid %>%
  mutate(gender = str_to_lower(gender),
         gender = ifelse(gender == "unknown", NA, gender),
         gender = as.factor(gender))
```

Use `covid` to calculate the ratio of the number of patients who are currently hospitalized to the number of patients who have ever been hospitalized.

```{r hospitalized_ratio}
covid %>% 
  mutate(across(c(currently_hospitalized, ever_hospitalized), function(x) x == "Yes"))  %>%
  summarise(across(c(currently_hospitalized, ever_hospitalized), sum)) %>%
  mutate(rate = currently_hospitalized / ever_hospitalized)
```

Use `covid` to create a summary showing the number of confirmed reports per month in 2020.

```{r confirmed_monthly_2020}
covid %>% 
  filter(classification == "CONFIRMED") %>% 
  mutate(month = month(reported_date, label = T)) %>% 
  count(classification, month)
```

Construct a model showing how well the number of cases reported in one week predicts the number of cases hospitalised two weeks later.
(You may find the `lag()` function useful. Checkout the n parameter!)

```{r correlation}
covid %>% 
  mutate(year_week= week(reported_date)) %>% 
  count(year_week) %>%
  mutate(two_weeks_earlier = lag(year_week, 2),
         n_two_weeks_earlier = lag(n, 2)) %>%
  ggplot(aes(n_two_weeks_earlier, n)) +
  geom_smooth()

```

```{r correlation_2}
# alternatively you can use joins

covid %>% 
  mutate(year_week= week(reported_date)) %>% 
  count(year_week) %>%
  mutate(two_weeks_later = year_week + 2) %>%
  left_join(covid %>% 
              mutate(year_week = week(reported_date)) %>% 
              count(year_week),
            by = c("two_weeks_later" = "year_week"),
            suffix = c("_earlier", "_later")) %>%
  ggplot(aes(n_earlier, n_later)) +
  geom_smooth()

```

Create a stacked bar chart with the age groups on the X axis showing the fraction of cases of each source. Facet the plot by gender:

```{r stacked_bar_faced}
covid %>%
  count(age_group, gender) %>%
  ggplot(aes("cases", n, fill = age_group)) +
  geom_col() + 
  facet_wrap(~gender)
```


Count the number of days in 2020 in which the number of reported cases was higher than the number reported the day before.

```{r days_of_increase}
covid %>% 
  count(reported_date) %>%
  mutate(day_before = reported_date - days(1)) %>%
  left_join(covid %>% 
              count(reported_date),
            by = c("day_before" = "reported_date"),
            suffix = c("_after", "_before")) %>%
  mutate(next_higher = n_before < n_after) %>%
  pull(next_higher) %>%
  sum(na.rm = T)
```

Create a new tibble called `history` showing the number of cases per month for each postal code prefix.
You may display the month using its full name (e.g., "September") or as a number (e.g., "09").

```{r create_history}
covid %>%
  mutate(month = month(reported_date, label = T, abbr = F)) %>%
  count(postal_code_prefix, month)
```

Rearrange the table you just created so that it has 13 columns: one called `postal_code_prefix` and one more for each month.
The first value in each row must be a postal code prefix;
the other values in that row must be the number of cases in that region and that month,
and missing values must be shown as 0 rather than NA.
Again, you may display the month using its full name or as a number.

```{r rearrange_table}
covid %>%
  mutate(month = month(reported_date, label = T, abbr = F)) %>%
  count(postal_code_prefix, month) %>%
  pivot_wider(names_from =  month,
              values_from = n,
              values_fill = 0)
```

The file `classification.xlsx` classifies age ranges into four groups.
Read this file to create a tibble called `classification`.

```{r read_data_xlsx}
(classification <- readxl::read_excel("data/classification.xlsx"))
```

Use this tibble and the `covid` tibble to create a new tibble with one column containing the age classification, one called `earliest_reported` showing the first date of a report for that age group, and one called `largest_delay` showing the largest difference (in days) between the episode date and the reported date within that age group.

```{r summarize_classified}
covid %>% 
  mutate(age = str_remove(age_group, " Years"),
         gap = reported_date - episode_date) %>%
  group_by(age) %>%
  summarise(earliest_reported = min(reported_date),
            largest_delay = max(gap)) %>%
  left_join(classification)
```