---
title: "Visual Editor"
author: "Thomas Koentges"
date: "26/11/2021"
output:
  bookdown::pdf_document2: default
bibliography: references.bib
csl: chicago-manual-of-style-17th-edition.csl
link-citation: yes
classoption:
- onecolumn
toc: false
---

# Visual Editing

Visual Editing gives you the comfort of a **Word Processor**. You don't have to write markdown. You can highlight `code` and still add code chunks:

```{r}
print("Hello World")
```

Learn all kinds of formats like ~~strikeout~~ and superscript^2^ and [small caps]{.smallcaps}. Citing is also super easy [@köntges2020].[^1] @köntges2020 says blah!

[^1]: But it is not a magic bullet!

*Inserting tables is not a pain anymore!*

| Needless Info I        | Needless Info 2                 |
|------------------------|---------------------------------|
| `print("hello world")` | will print "hello world"        |
| `1:2`                  | will generate an integer vector |

: My awesome table

## Math is easier to

**CMD + /**

You can write: $i 8 \sum{\pi}$ and it was salty. To which people might reply that's

$$
\sqrt{a^2 b^2 3}
$$

or ab-surd <!--# Puns made me numb, math puns make me number! -->.

------------------------------------------------------------------------

> Meaningful-quote options are there too!

You can also insert plots and reference them (see \@ref(fig:diamond-plot))

```{r diamond-plot, fig.cap="The cars data.", warning=F, message=F, echo=F}
library(tidyverse)
ggplot(diamonds) + geom_point(aes(price, carat))
```

### Links for Working with the Visual Editor

-   [RMarkdown Basics](https://rmarkdown.rstudio.com/authoring_basics.html)

-   [Overview Visual Editor](https://rstudio.github.io/visual-markdown-editing/)

-   [RMarkdown Cheat Sheet 2021](https://raw.githubusercontent.com/rstudio/cheatsheets/main/rmarkdown.pdf)

-   [Cross Referencing](https://bookdown.org/yihui/rmarkdown-cookbook/cross-ref.html#)

-   [Math in RMarkdown](https://rpruim.github.io/s341/S19/from-class/MathinRmd.html)

### Links for Editing CSL files

-   [Zotero Style Archive](https://www.zotero.org/styles)

-   [CSL Visual Editor](https://editor.citationstyles.org/)

\newpage

# References
