---
title: "CodeChunks and more"
author: "Thomas Koentges"
date: "`r params$report_date`"
output: html_document
params:
  x_axis: "price"
  y_axis: "carat"
  report_date: "`r format(Sys.time(), '%Y, %B %d')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = T)
library(tidyverse)
comma <- function(x) format(x, digits = 2, big.mark = ",")

smaller <- diamonds %>% 
  filter(carat <= 2.5)
```

## Code Chunks

You can insert new code chunks in 4 ways:

1.  *CTRL/CMD + Alt/Option + I*
2.  Click +C
3.  Type opening and closing \`\`\`
4.  Use the Visual Editor

## How a code chunk looks

```` r
```{r chunk_name, echo=F}`r ''`
# if you read this code in the source file, this is not a code chunk!
library(dplyr)
mtcars %>% 
  group_by(cyl) %>% 
  summarize(n = n(), mean = mean(mpg))
```
````

```{r chunk_name, echo=F, eval=F}
# this would be a code chunk! But the code is neither printed (echo = F) nor executed (eval = F)
library(dplyr)
mtcars %>% 
  group_by(cyl) %>% 
  summarize(n = n(), mean = mean(mpg))
```

### How it works

```{r}
mtcars %>% 
  group_by(cyl) %>% 
  summarize(n = n(), mean = mean(mpg))
```

### Important chunk options

-   `eval = FALSE`

-   `include = FALSE`

-   `echo = FALSE`

-   `message = FALSE` or `warning = FALSE`

-   `results = 'hide'` and `fig.show = 'hide'`

-   `error = TRUE`

```{r cache=TRUE}
print("hello world")
```

-   `cache = TRUE`

## Cache example

```{r iris_data, cache=TRUE}
my_data <- iris %>%
  filter(Species != "setosa")
```

```{r iris_plot, cache = T, dependson="iris_data"}
my_plot <- my_data %>%
  ggplot(aes(Sepal.Width, col = Species)) +
  geom_boxplot()
```

```{r iris_vis}
my_plot
```

## Inline R

You can write R code inline to calculate variables. For instance: We have data about `r nrow(diamonds)` diamonds. Only `r nrow(diamonds) - nrow(smaller)` are larger than 2.5 carats.

## Exercises

1.  Make the numbers above nicer using the `comma()` function.

2.  Add a section that explores how diamond sizes vary by cut, colour, and clarity. Assume you're writing a report for someone who doesn't know R, and instead of setting echo = FALSE on each chunk, set a global option.

3.  Download diamond-sizes.Rmd from <https://github.com/hadley/r4ds/tree/master/rmarkdown>. Add a section that describes the largest 20 diamonds, including a table that displays their most important attributes.

4.  Set up a network of chunks where d depends on c and b, and both b and c depend on a. Have each chunk print lubridate::now(), set cache = TRUE, then verify your understanding of caching.

## Other interesting things

::: columns
::: {.column width="40%"}
#### Info in 2-columns

On the right side is a very informative figure!
:::

::: {.column width="60%"}
```{r diamond-plot, fig.cap="Something useful about diamonds", fig.width=4, fig.height=3, echo=F}
ggplot(diamonds, aes_string(params$x_axis, params$y_axis)) + geom_point()
```
:::
:::

## Exercise

A co-worker has sent you the file `rmd-country-profile.Rmd`, which is an R Markdown document analyzing the data in `at_health_facilities.csv` for Bangladesh. They could not knit the file, and are providing you with the raw `.Rmd` file instead of a rendered file.

1.  Go through the file, fixing things that are preventing it from knitting cleanly.
2.  Change the two lines of bold text to H2-level headers to organize the document, and add a table of contents.
3.  Convert this R Markdown report for Bangladesh into a parameterized report with the country's iso3 code as its parameter. Knit a new country profile for Egypt (ISO3 code "EGY").
